### 2022-11-24 paper3.tex
paper 3 supplement

   \node[rectangle, draw, rounded corners = 0.2em] (externalknowl) [below = 2em of external]
   {\begin{tabular}{l}
      \multicolumn{1}{c}{\textbf{External knowledge}} \\
     {\scriptsize -- between-study heterogeneity} \\
     {\scriptsize -- skepticism regarding original study} \\
     {\scriptsize -- data from other studies} \\
     {\scriptsize $\phantom{\rightarrow} \hdots$} \\
   \end{tabular}};

@@

At least three common types of external knowledge can be distinguished in the
replication setting: (i) expected heterogeneity between original and replication
study due to differences in study design, execution, and population, (ii) prior
knowledge about the effect size either from theory or from related studies,
(iii) skepticism regarding the original study due to the possibility of
exaggerated results.

@@

\subsubsection{The skeptical \textit{p}-value}
\citet{Held2020} proposed a reverse-Bayes approach for quantifying replication
success. The main idea is to determine the variance of a ``skeptical'' zero-mean
normal prior for the effect size $\theta$ such that its posterior distribution
based on the original study is no longer credible. Replication success is then
achieved if the replication data are in conflict with the skeptical prior. The
procedure can be summarized by a ``skeptical $p$-value'' $\ps$, and the lower
the $p$-value the higher the degree of replication success. \citet[sec.
2.1]{Held2021} showed that the success region for replication success defined by
$\ps \leq \alpha$ is given by
\begin{align}
  \label{eq:Pssuccess}
  S_{\scriptscriptstyle \ps}
  = \left[\zalpha \sqrt{\sigma^{2}_{r} +
  \frac{\sigma^{2}_{o}}{(z_{o}^{2}/\zalpha^{2}) - 1}}, \infty\right).
\end{align}
From the success region~\eqref{eq:Pssuccess} the probability of replication
success at level $\alpha$ is
\begin{align*}
  \Pr(\that_r \in S_{\scriptscriptstyle \ps} \given \that_{o}, \sigma_{o}, \sigma_{r})
  &=%  \Phi\left(\frac{\muthatr - \zalpha \sqrt{\sigma^{2}_{r} +
    % \sigma^{2}_{o}/\{(z_{o}^{2}/\zalpha^{2}) - 1}\}}{\sqrt{\sigma^{2}_{r} +
    % \tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right),
     \Phi\left(\frac{\muthatr - \zalpha \sqrt{\sigma^{2}_{r} +
    \sigma^{2}_{o}/\{(z_{o}^{2}/\zalpha^{2}) - 1}\}}{\sigmathatr}\right),
\end{align*}
and also bounded from above by a constant
$\text{limPr}_{\scriptscriptstyle \ps} = \lim_{\sigma_{r} \downarrow 0} \Pr(\that_r \in S_{\scriptscriptstyle \ps} \given \that_{o}, \sigma_{o}, \sigma_{r})$.
As for the two-trials rule, the required standard error $\sigma_{r}^{*}$ to
achieve a probability of replication success
$1 - \beta < \text{limPr}_{\scriptscriptstyle \ps}$ can be computed analytically
for $\alpha < \beta$:
\begin{align*}
  \sigma_{r}^{*} = \sqrt{x^{2} - \frac{\sigma^{2}_{o}}{(z_{o}/\zalpha)^{2} - 1}}
\end{align*}
with
\begin{align*}
  x = \frac{\zalpha \muthatr - \zbeta \sqrt{\muthatr^{2} - (\zalpha^{2} - \zbeta^{2})
  [\tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g) - \sigma^{2}_{o}/\{(z_{o}/\zalpha)^{2}
  - 1\}]}}{\zalpha^{2} - \zbeta^{2}}.
\end{align*}

\subsubsection{The skeptical Bayes factor}
\citet{Pawel2022b} modified the previously described reverse-Bayes assessment of
replication success from \citet{Held2020} to work with Bayes factors instead of
tail probabilities as measures of evidence and prior data conflict. Again, the
procedure can be summarized in a single measure termed the ``skeptical Bayes
factor'' $\BFs$, with lower values of $\BFs$ pointing to higher degrees of
replication success. Also for this method, the success region and the
probability of replication success can be expressed in closed-form but the
derivations are more involved than for the other methods. For this reason, they
are only given in the supplement.

@@

We will now revisit the experiment ``Labels'' % from
% Section~\ref{sec:example}
and compute the probability of replication success.
% and
% the replication sample size
% based on the previously discussed analysis methods.
The parameters of the analysis methods are specified as follows: For the
two-trials rule we use the conventional one-sided significance level
$\alpha = 0.025$, while for meta-analysis we use the more
stringent level $\alpha = 0.025^{2}$ as the
method is based on two data sets rather than one. We use a
$1 - \alpha = 90\%$ confidence interval which is
conventionally used in equivalence testing, along with a margin
$\Delta = 0.2$ corresponding to a small SMD effect size according to
the classification from \citet{Cohen1992}. For the skeptical $p$-value we use
the recommended ``golden'' level $\alpha = 0.062$ as it
guarantees that for original studies which where just significant at
$\alpha = 0.025$ replication success is only possible if the replication effect
estimate is larger than the original one \citep{Held2021}. Finally, for the
replication Bayes factor and the skeptical Bayes factor we use the ``strong
evidence'' level $\gamma = 1/10$ from \citet{Jeffreys1961}.

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{images/paper3/example-applied-1}
\end{knitrout}
\caption{Probability of replication success as a function of relative sample
  size $c = n_{r}/n_{o}$ for experiment ``Labels'' with original
  effect estimate $\hat{\theta}_{o} = 0.205$ and
  standard error $\sigma_{o} = 0.051$ for
  different initial prior parameters ($\tau, \mutheta, \sigmatheta^{2}$). The
  probability of replication success with the design prior
  $\tau = 0, \mutheta = 0$, and $\sigmatheta^{2} = 0$ (right plot) corresponds
  to the type I error rate under the fixed effects null hypothesis
  ($H_{0}\colon \theta = 0, \tau^{2} = 0$). Replication success is defined by
  the two-trials rule at level $\alpha = 0.025$, the replication
  Bayes factor at level $\gamma = 1/10$, fixed effects-meta
  analysis at level $\alpha = 0.025^{2}$, effect size
  equivalence based on $90\%$ confidence interval and with
  margin $\Delta = 0.2$, skeptical $p$-value at level
  $\alpha = 0.062$, and skeptical Bayes factor at level
  $\gamma = 1/10$.}
\label{fig:example}
\end{figure}
Figure~\ref{fig:example} shows the probability of replication success as a
function of the relative sample size $c = n_{r}/n_{o}$ and for different initial
priors. The left and middle plot are based on an uninformative prior for the
effect size ($\sigmatheta^{2} \to \infty$) without heterogeneity ($\tau^{2} = 0$)
and with heterogeneity ($\tau^{2} = 0.05^{2}$),
respectively. The right plot shows the prior corresponding to the ``fixed
effects null hypothesis'' $H_{0} \colon \theta = 0, \tau^{2} =
0$, %, \ie{} the effect size
% $\theta$ is a point mass at zero and there is no heterogeneity,
so that the probability of replication success is the type I error rate which
some stakeholders might require to be ``controlled'' at some adequate level.

We see from the left and middle plots that increasing the relative sample size
monotonically increases the probability of replication success for all methods
but meta-analysis (light blue). Meta-analysis shows a non-monotone behavior
because the original study was already highly significant so that the pooled
effect estimate is significant even for replication studies with very small
sample size \citep{Micheloud2020}. The uncertainty regarding the replication
effect estimate $\that_{r}$ may therefore even reduce the probability of
replication success for meta-analysis if the sample size is increased. If
heterogeneity is taken into account (middle plot) the probability of replication
success becomes closer to 50\% for all methods but the equivalence test,
reflecting the larger uncertainty about the effect size $\theta$. To achieve
$80\%$ probability of replication success the fewest
samples are required with meta-analysis, followed by the skeptical $p$-value,
the two-trials rule, the replication Bayes factor, the skeptical Bayes factor,
and lastly the equivalence test. If the chosen sample size should guarantee a
sufficiently conclusive replication study with all these methods, the
replication sample size has to be slightly larger than the original one in the
situation of no heterogeneity ($\tau^{2} = 0$), while it has to be increased
more than ten-fold if there is heterogeneity
($\tau^{2} = 0.05^{2}$). However, this is mostly due to the
equivalence test which requires by far the most samples. If the equivalence test
sample size is ignored, the relative sample size
$c = 2.5$ ensures at least
$80\%$ probability of replication success with the
remaining methods.

The right plot in Figure~\ref{fig:example} shows that the type I error rate of
the two-trials rule (black) stays constant at
$\alpha = 0.025$, as expected by definition of the method.
In contrast, the type I error rates of the other methods vary with the relative
sample size $c$ but most of them stay below
$\alpha = 0.025$ for all $c$ with the exception of
meta-analysis and the skeptical $p$-value. Meta-analysis (light blue) has an
extremely high type I error rate as the pooling with the highly significant
original data leads to replication success if the replication sample size is not
drastically increased. The type I error rate of the skeptical $p$-value (yellow)
is only slightly larger than $\alpha = 0.025$ which is
expected since the level $\alpha = 0.062$ is used for
declaring replication success with the skeptical $p$-value, and its type I error
rate is always smaller than the level for thresholding it \citep{Held2020}. The
type I error rate of the skeptical $p$-value decreases to values smaller than
$\alpha = 0.025$ of the two-trials rule at approximately
$c = 3$.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{images/paper3/ssd-protzko-1}
\end{knitrout}
\caption{The left plot shows the required relative sample size $c = n_r/n_o$ to
  achieve a target probability of replication success of
  $1 - \beta = 80$\% (if possible). Replication success
  is defined through the two-trials rule at level $\alpha = 0.025$,
  replication Bayes factor at level $\gamma = 1/10$, fixed
  effects-meta analysis at level $\alpha = 0.025^{2}$,
  effect size equivalence at level $\alpha = 0.1$ with margin
  $\Delta = 0.2$, skeptical $p$-value at level
  $\alpha = 0.062$, and skeptical Bayes factor at level
  $\gamma = 1/10$ for data from the replication project by
  \citet{Protzko2020}. A flat initial prior
  ($\mutheta = 0, \sigmatheta^{2} \to \infty$) is used for the effect size
  $\theta$ is used either without ($\tau = 0$) or with heterogeneity
  ($\tau = 0.05$). The right plot shows the type I error
  rate associated with the required sample size. Experiments are ordered (top to
  bottom) by their original one-sided $p$-value
  $p_{o} = 1 - \Phi(|\hat{\theta}_{o}|/\sigma_{o}$).}
\label{fig:ssd-all}
\end{figure}

@@

We see that for all methods but the equivalence test the required relative
sample size $c$ decreases with decreasing original $p$-value $p_{o}$, and
original studies with very small $p$-values require much fewer samples in the
replication study. For the equivalence test, the required sample size depends
instead on the size of the original standard error $\sigma_{o}$, and smaller
standard errors leads to smaller required sample sizes in the
replication. % For instance, the
% experiment ``Orientation'' with the original standard error $\sigma_{o} = 0.045$
% requires much less samples than the experiment ``Self-Control'' with original
% standard error $\sigma_{o} = 0.052$.
We also see that taking into account heterogeneity (triangle) increases the
required sample size for all methods compared to not taking it into account
(dot). At the same time, a larger required sample size reduces the type I error
rate for most methods. We see again the pattern that the type I error rate of
the equivalence test and the skeptical $p$-value is larger than the type I error
rate 2.5\% of the two-trials rule. However, while the type I error rate of the
skeptical $p$-value decreases when replication studies require larger sample
sizes, the type I error rate of the equivalence test may also be large if the
replication requires very large sample sizes (\eg{} for the experiment ``FSD'')
since it depends on whether the original effect estimate $\that_{o}$ is
sufficiently different from zero. If the original effect estimate $\that_{o}$ is
close to zero, the type I error rate of the equivalence test is drastically
increased as equivalence can also be established if the effect estimates from
original and replication studies are close to zero (as under the null
hypothesis).

Taken together, for most of the experiments all methods but the equivalence test
require fewer samples in the replication than in the original study to achieve a
target probability of replication success
$1 - \beta = 80$\%. This is still the case if
heterogeneity is taken into account in the design prior (triangles), which
generally increases the required sample size compared to when heterogeneity is
not taken into account (dots), especially for studies with large original
$p$-value. Larger replication sample sizes are required for some original
studies. In some cases these are unrealistically large (\eg{} in the experiment
``Prediction'' an almost 30 times increase in sample size for the replication
Bayes factor), but in other cases they seem more realistic and could be
reallocated from the other studies which require fewer samples (\eg{} in the
experiment ``Referrals'' an almost three times increase for the skeptical Bayes
factor). On the other hand, the equivalence test typically requires larger
sample sizes in the replication because the original standard errors are large
relative to the specified margin. If one anticipates to analyze the original and
replication pair with an equivalence test, this should therefore be taken into
account already at the design stage of the original study.

@@

\end{subappendices}

>>>>

   \node[rectangle, draw, rounded corners = 0.2em] (externalknowl) [below = 2em of external]
   {\begin{tabular}{l}
      \multicolumn{1}{c}{\textbf{External knowledge}} \\
     {\scriptsize -- between-study heterogeneity} \\
     {\scriptsize -- scepticism regarding original study} \\
     {\scriptsize -- data from other studies} \\
     {\scriptsize $\phantom{\rightarrow} \hdots$} \\
   \end{tabular}};

@@

At least three common types of external knowledge can be distinguished in the
replication setting: (i) expected heterogeneity between original and replication
study due to differences in study design, execution, and population, (ii) prior
knowledge about the effect size either from theory or from related studies,
(iii) scepticism regarding the original study due to the possibility of
exaggerated results.

@@

\subsubsection{The sceptical \textit{p}-value}
\citet{Held2020} proposed a reverse-Bayes approach for quantifying replication
success. The main idea is to determine the variance of a ``sceptical'' zero-mean
normal prior for the effect size $\theta$ such that its posterior distribution
based on the original study is no longer credible. Replication success is then
achieved if the replication data are in conflict with the sceptical prior. The
procedure can be summarized by a ``sceptical $p$-value'' $\ps$, and the lower
the $p$-value the higher the degree of replication success. \citet[sec.
2.1]{Held2021} showed that the success region for replication success defined by
$\ps \leq \alpha$ is given by
\begin{align}
  \label{eq:Pssuccess}
  S_{\scriptscriptstyle \ps}
  = \left[\zalpha \sqrt{\sigma^{2}_{r} +
  \frac{\sigma^{2}_{o}}{(z_{o}^{2}/\zalpha^{2}) - 1}}, \infty\right).
\end{align}
From the success region~\eqref{eq:Pssuccess} the probability of replication
success at level $\alpha$ is
\begin{align*}
  \Pr(\that_r \in S_{\scriptscriptstyle \ps} \given \that_{o}, \sigma_{o}, \sigma_{r})
  &=%  \Phi\left(\frac{\muthatr - \zalpha \sqrt{\sigma^{2}_{r} +
    % \sigma^{2}_{o}/\{(z_{o}^{2}/\zalpha^{2}) - 1}\}}{\sqrt{\sigma^{2}_{r} +
    % \tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right),
     \Phi\left(\frac{\muthatr - \zalpha \sqrt{\sigma^{2}_{r} +
    \sigma^{2}_{o}/\{(z_{o}^{2}/\zalpha^{2}) - 1}\}}{\sigmathatr}\right),
\end{align*}
and also bounded from above by a constant
$\text{limPr}_{\scriptscriptstyle \ps} = \lim_{\sigma_{r} \downarrow 0} \Pr(\that_r \in S_{\scriptscriptstyle \ps} \given \that_{o}, \sigma_{o}, \sigma_{r})$.
As for the two-trials rule, the required standard error $\sigma_{r}^{*}$ to
achieve a probability of replication success
$1 - \beta < \text{limPr}_{\scriptscriptstyle \ps}$ can be computed analytically
for $\alpha < \beta$:
\begin{align*}
  \sigma_{r}^{*} = \sqrt{x^{2} - \frac{\sigma^{2}_{o}}{(z_{o}/\zalpha)^{2} - 1}}
\end{align*}
with
\begin{align*}
  x = \frac{\zalpha \muthatr - \zbeta \sqrt{\muthatr^{2} - (\zalpha^{2} - \zbeta^{2})
  [\tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g) - \sigma^{2}_{o}/\{(z_{o}/\zalpha)^{2}
  - 1\}]}}{\zalpha^{2} - \zbeta^{2}}.
\end{align*}

\subsubsection{The sceptical Bayes factor}
\citet{Pawel2022b} modified the previously described reverse-Bayes assessment of
replication success from \citet{Held2020} to work with Bayes factors instead of
tail probabilities as measures of evidence and prior data conflict. Again, the
procedure can be summarized in a single measure termed the ``sceptical Bayes
factor'' $\BFs$, with lower values of $\BFs$ pointing to higher degrees of
replication success. Also for this method, the success region and the
probability of replication success can be expressed in closed-form but the
derivations are more involved than for the other methods. For this reason, they
are only given in the supplement.

@@

We will now revisit the experiment ``Labels'' % from
% Section~\ref{sec:example}
and compute the probability of replication success.
% and
% the replication sample size
% based on the previously discussed analysis methods.
The parameters of the analysis methods are specified as follows: For the
two-trials rule we use the conventional one-sided significance level
$\alpha = 0.025$, while for meta-analysis we use the more
stringent level $\alpha = 0.025^{2}$ as the
method is based on two data sets rather than one. We use a
$1 - \alpha = 90\%$ confidence interval which is
conventionally used in equivalence testing, along with a margin
$\Delta = 0.2$ corresponding to a small SMD effect size according to
the classification from \citet{Cohen1992}. For the sceptical $p$-value we use
the recommended ``golden'' level $\alpha = 0.062$ as it
guarantees that for original studies which where just significant at
$\alpha = 0.025$ replication success is only possible if the replication effect
estimate is larger than the original one \citep{Held2021}. Finally, for the
replication Bayes factor and the sceptical Bayes factor we use the ``strong
evidence'' level $\gamma = 1/10$ from \citet{Jeffreys1961}.

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{images/paper3/example-applied-1}
\end{knitrout}
\caption{Probability of replication success as a function of relative sample
  size $c = n_{r}/n_{o}$ for experiment ``Labels'' with original
  effect estimate $\hat{\theta}_{o} = 0.205$ and
  standard error $\sigma_{o} = 0.051$ for
  different initial prior parameters ($\tau, \mutheta, \sigmatheta^{2}$). The
  probability of replication success with the design prior
  $\tau = 0, \mutheta = 0$, and $\sigmatheta^{2} = 0$ (right plot) corresponds
  to the type I error rate under the fixed effects null hypothesis
  ($H_{0}\colon \theta = 0, \tau^{2} = 0$). Replication success is defined by
  the two-trials rule at level $\alpha = 0.025$, the replication
  Bayes factor at level $\gamma = 1/10$, fixed effects-meta
  analysis at level $\alpha = 0.025^{2}$, effect size
  equivalence based on $90\%$ confidence interval and with
  margin $\Delta = 0.2$, sceptical $p$-value at level
  $\alpha = 0.062$, and sceptical Bayes factor at level
  $\gamma = 1/10$.}
\label{fig:example}
\end{figure}
Figure~\ref{fig:example} shows the probability of replication success as a
function of the relative sample size $c = n_{r}/n_{o}$ and for different initial
priors. The left and middle plot are based on an uninformative prior for the
effect size ($\sigmatheta^{2} \to \infty$) without heterogeneity ($\tau^{2} = 0$)
and with heterogeneity ($\tau^{2} = 0.05^{2}$),
respectively. The right plot shows the prior corresponding to the ``fixed
effects null hypothesis'' $H_{0} \colon \theta = 0, \tau^{2} =
0$, %, \ie{} the effect size
% $\theta$ is a point mass at zero and there is no heterogeneity,
so that the probability of replication success is the type I error rate which
some stakeholders might require to be ``controlled'' at some adequate level.

We see from the left and middle plots that increasing the relative sample size
monotonically increases the probability of replication success for all methods
but meta-analysis (light blue). Meta-analysis shows a non-monotone behavior
because the original study was already highly significant so that the pooled
effect estimate is significant even for replication studies with very small
sample size \citep{Micheloud2020}. The uncertainty regarding the replication
effect estimate $\that_{r}$ may therefore even reduce the probability of
replication success for meta-analysis if the sample size is increased. If
heterogeneity is taken into account (middle plot) the probability of replication
success becomes closer to 50\% for all methods but the equivalence test,
reflecting the larger uncertainty about the effect size $\theta$. To achieve
$80\%$ probability of replication success the fewest
samples are required with meta-analysis, followed by the sceptical $p$-value,
the two-trials rule, the replication Bayes factor, the sceptical Bayes factor,
and lastly the equivalence test. If the chosen sample size should guarantee a
sufficiently conclusive replication study with all these methods, the
replication sample size has to be slightly larger than the original one in the
situation of no heterogeneity ($\tau^{2} = 0$), while it has to be increased
more than ten-fold if there is heterogeneity
($\tau^{2} = 0.05^{2}$). However, this is mostly due to the
equivalence test which requires by far the most samples. If the equivalence test
sample size is ignored, the relative sample size
$c = 2.5$ ensures at least
$80\%$ probability of replication success with the
remaining methods.

The right plot in Figure~\ref{fig:example} shows that the type I error rate of
the two-trials rule (black) stays constant at
$\alpha = 0.025$, as expected by definition of the method.
In contrast, the type I error rates of the other methods vary with the relative
sample size $c$ but most of them stay below
$\alpha = 0.025$ for all $c$ with the exception of
meta-analysis and the sceptical $p$-value. Meta-analysis (light blue) has an
extremely high type I error rate as the pooling with the highly significant
original data leads to replication success if the replication sample size is not
drastically increased. The type I error rate of the sceptical $p$-value (yellow)
is only slightly larger than $\alpha = 0.025$ which is
expected since the level $\alpha = 0.062$ is used for
declaring replication success with the sceptical $p$-value, and its type I error
rate is always smaller than the level for thresholding it \citep{Held2020}. The
type I error rate of the sceptical $p$-value decreases to values smaller than
$\alpha = 0.025$ of the two-trials rule at approximately
$c = 3$.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{images/paper3/ssd-protzko-1}
\end{knitrout}
\caption{The left plot shows the required relative sample size $c = n_r/n_o$ to
  achieve a target probability of replication success of
  $1 - \beta = 80$\% (if possible). Replication success
  is defined through the two-trials rule at level $\alpha = 0.025$,
  replication Bayes factor at level $\gamma = 1/10$, fixed
  effects-meta analysis at level $\alpha = 0.025^{2}$,
  effect size equivalence at level $\alpha = 0.1$ with margin
  $\Delta = 0.2$, sceptical $p$-value at level
  $\alpha = 0.062$, and sceptical Bayes factor at level
  $\gamma = 1/10$ for data from the replication project by
  \citet{Protzko2020}. A flat initial prior
  ($\mutheta = 0, \sigmatheta^{2} \to \infty$) is used for the effect size
  $\theta$ is used either without ($\tau = 0$) or with heterogeneity
  ($\tau = 0.05$). The right plot shows the type I error
  rate associated with the required sample size. Experiments are ordered (top to
  bottom) by their original one-sided $p$-value
  $p_{o} = 1 - \Phi(|\hat{\theta}_{o}|/\sigma_{o}$).}
\label{fig:ssd-all}
\end{figure}

@@

We see that for all methods but the equivalence test the required relative
sample size $c$ decreases with decreasing original $p$-value $p_{o}$, and
original studies with very small $p$-values require much fewer samples in the
replication study. For the equivalence test, the required sample size depends
instead on the size of the original standard error $\sigma_{o}$, and smaller
standard errors leads to smaller required sample sizes in the
replication. % For instance, the
% experiment ``Orientation'' with the original standard error $\sigma_{o} = 0.045$
% requires much less samples than the experiment ``Self-Control'' with original
% standard error $\sigma_{o} = 0.052$.
We also see that taking into account heterogeneity (triangle) increases the
required sample size for all methods compared to not taking it into account
(dot). At the same time, a larger required sample size reduces the type I error
rate for most methods. We see again the pattern that the type I error rate of
the equivalence test and the sceptical $p$-value is larger than the type I error
rate 2.5\% of the two-trials rule. However, while the type I error rate of the
sceptical $p$-value decreases when replication studies require larger sample
sizes, the type I error rate of the equivalence test may also be large if the
replication requires very large sample sizes (\eg{} for the experiment ``FSD'')
since it depends on whether the original effect estimate $\that_{o}$ is
sufficiently different from zero. If the original effect estimate $\that_{o}$ is
close to zero, the type I error rate of the equivalence test is drastically
increased as equivalence can also be established if the effect estimates from
original and replication studies are close to zero (as under the null
hypothesis).

Taken together, for most of the experiments all methods but the equivalence test
require fewer samples in the replication than in the original study to achieve a
target probability of replication success
$1 - \beta = 80$\%. This is still the case if
heterogeneity is taken into account in the design prior (triangles), which
generally increases the required sample size compared to when heterogeneity is
not taken into account (dots), especially for studies with large original
$p$-value. Larger replication sample sizes are required for some original
studies. In some cases these are unrealistically large (\eg{} in the experiment
``Prediction'' an almost 30 times increase in sample size for the replication
Bayes factor), but in other cases they seem more realistic and could be
reallocated from the other studies which require fewer samples (\eg{} in the
experiment ``Referrals'' an almost three times increase for the sceptical Bayes
factor). On the other hand, the equivalence test typically requires larger
sample sizes in the replication because the original standard errors are large
relative to the specified margin. If one anticipates to analyze the original and
replication pair with an equivalence test, this should therefore be taken into
account already at the design stage of the original study.

@@

\section{Supplementary material}

Here, we provide additional information on computing the predictive distribution
of the replication effect estimate when a prior is assigned to the heterogeneity
variance $\tau^{2}$ (Section~\ref{sec:priortau}). We also provide additional
information on methods for analyzing replication data. For each method we derive
the \emph{success region} in terms of the effect estimate of the replication
study $\that_{r}$, which is required for sample size determination as
illustrated in the main manuscript (Section~\ref{sec:2TR} to~\ref{sec:BFs}). For
the two-trials rule and the replication Bayes factor methods we additionally
provide derivations on how these methods can be generalized to the multisite
replication setting. We show then how the optimal number of samples per site can
be derived for multisite SSD (Section~\ref{sec:multi}). Finally, we show SSD for
the \citet{Protzko2020} project but using an adaptive shrinkage prior instead of
the flat prior as in the main manuscript (Section~\ref{sec:ssdprotzko}).

\subsection{Prior on the heterogeneity variance}
\label{sec:priortau}
When also a prior is assigned to the heterogeneity variance $\tau^{2}$, the
predictive distribution of the replication effect estimate $\that_{r}$ is given
by
\begin{align*}
  f(\that_{r} \given \that_{o}, \sigma_{o}, \sigma_{r})
  &= \int_{0}^{+\infty} f(\that_{r} \given \sigma_{r}, \that_{o}, \sigma_{o},
    \tau^{2}) \,
    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\tau^{2}.
\end{align*}
That is, it is the predictive distribution of the replication effect estimate
$\that_{r}$ integrated with respect to the marginal posterior of $\tau^{2}$
based on the original data $x_{o} = \{\that_{o}, \sigma^{2}_{o}\}$. If the
initial prior for $\theta$ is normal
$\theta \sim \Nor(\mutheta, \sigmatheta^{2})$, and the initial prior for
$\tau^{2}$ has density $f(\tau^{2})$, we have
\begin{align*}
  f(\tau^{2} \given \that_{o}, \sigma_{o})
  &= \int_{-\infty}^{+\infty} f(\theta, \tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\theta \\
  &= \frac{\int_{-\infty}^{+\infty} f(\that_{o} \given \theta, \tau^{2}, \sigma^{2}_{o}) \,
    f(\theta \given \tau^{2}) \, f(\tau^{2}) \, \text{d}\theta}{\int_{0}^{+\infty}
    \int_{-\infty}^{+\infty} f(\that_{o} \given \theta_{*}, \tau^{2}_{*}, \sigma^{2}_{o}) \,
    f(\theta_{*} \given \tau^{2}_{*}) \, f(\tau^{2}_{*}) \, \text{d}\theta_{*} \,
    \text{d}\tau^{2}_{*}} \\
  &= \frac{f(\tau^{2}) \int_{-\infty}^{+\infty} \Nor(\that_{o} \given \theta, \tau^{2}
    + \sigma^{2}_{o}) \, \Nor(\theta \given \mutheta, \sigmatheta^{2}) \,\text{d}\theta
    }{\int_{0}^{+\infty} f(\tau^{2}_{*})
    \int_{-\infty}^{+\infty} \Nor(\that_{o} \given \theta_{*}, \tau^{2}_{*} + \sigma^{2}_{o}) \,
    \Nor(\theta_{*} \given \mutheta, \sigmatheta^{2}) \, \text{d}\theta_{*} \,
    \text{d}\tau^{2}_{*}} \\
  &= \frac{f(\tau^{2}) \, \Nor(\that_{o} \given \mutheta, \tau^{2}
    + \sigma^{2}_{o} + \sigmatheta^{2})
    }{\int_{0}^{+\infty} f(\tau^{2}_{*})
    \Nor(\that_{o} \given \mutheta, \tau^{2}_{*} + \sigma^{2}_{o} + \sigmatheta^{2}) \,
    \text{d}\tau^{2}_{*}}.
\end{align*}
To compute the marginal posterior density of $\tau^{2}$ one numerical
integration is hence required. The updating of the prior depends on the distance
between prior mean $\mutheta$ and the original effect estimate $\that_{o}$
relative to the prior variance $\sigmatheta^{2}$ and the squared standard error
$\sigma_{o}^{2}$. If an improper uniform prior is assigned to $\theta$
($\sigmatheta^{2} \to \infty$), the posterior reduces to the prior
\begin{align*}
  \lim_{\sigmatheta^{2} \to \infty} f(\tau^{2} \given \that_{o}, \sigma_{o})
  &= \lim_{\sigmatheta^{2} \to \infty} \frac{f(\tau^{2}) \, \Nor(\that_{o} \given \mutheta, \tau^{2}
    + \sigma^{2}_{o} + \sigmatheta^{2})
    }{\int_{0}^{+\infty} f(\tau^{2}_{*})
    \Nor(\that_{o} \given \mutheta, \tau^{2}_{*} + \sigma^{2}_{o} + \sigmatheta^{2}) \,
    \text{d}\tau^{2}_{*}} \\
  &= \lim_{\sigmatheta^{2} \to \infty}  \int_{0}^{+\infty} \frac{f(\tau^{2})}{f(\tau^{2}_{*})} \,
    \underbrace{\sqrt{\frac{\tau^{2}_{*} + \sigma^{2}_{o} + \sigmatheta^{2}}{\tau^{2} + \sigma^{2}_{o} +
    \sigmatheta^{2}}}}_{\to 1} \, \exp\bigg[-\frac{1}{2}\bigg\{\underbrace{
    \frac{(\that_{o} - \mutheta)^{2}}{\tau^{2} + \sigma^{2}_{o} + \sigmatheta^{2}}}_{\downarrow 0} -
    \underbrace{\frac{(\that_{o} - \mutheta)^{2}}{\tau^{2}_{*} + \sigma^{2}_{o} +
    \sigmatheta^{2}}}_{\downarrow 0} \bigg\}\bigg] \, \text{d}\tau^{2}_{*} \\
  &= f(\tau^{2}),
\end{align*}
the limit can be interchanged with the integral because of the monotone
convergence theorem. This means that with a uniform prior nothing can be learned
about the variance $\tau^{2}$ which intuitively makes sense as estimation of a
variance requires at least two observations. The phenomenon is illustrated in
Figure~\ref{fig:margposttau2} for the data from the experiment ``Labels''
\citep{Protzko2020} as also used in the main manuscript. We see that as the
prior standard deviation increases (making the prior more uniform), the marginal
posterior density becomes closer to the prior density.
\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{images/paper3/sup-tau-random-example-1}
\end{knitrout}
\caption{Marginal posterior distribution of heterogeneity variance $\tau^{2}$
  based on data from experiment ``Labels'' from \citet{Protzko2020} with
  original effect estimate $\hat{\theta}_{o} = 0.205$ and
  standard error $\sigma_{o} = 0.051$. A
  $\theta \sim \Nor(0, \sigmatheta^{2})$ prior is assigned to the
  effect size $\theta$ and a half normal prior with standard deviation
  $0.04$ is assigned to $\tau$.}
\label{fig:margposttau2}
\end{figure}

Combining all the previous results, we obtain the probability of replication
success as
\begin{align*}
  \Pr(\that_{r} \in S \given \that_{o}, \sigma_{o}, \sigma_{r})
  &= \int_{S}\int_{0}^{+\infty} f(\that_{r} \given \that_{o}, \sigma_{o}, \sigma_{r}, \tau^{2}) \,
    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\that_{r} \,\text{d}\tau^{2} \\
  &= \int_{0}^{+\infty} \Pr(\that_{r} \in S \given \that_{o}, \sigma_{o}, \sigma_{r}, \tau^{2}) \,
    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\tau^{2}. \\
\end{align*}
This mean computing the probability of replication success with a prior on
$\tau^{2}$ requires two-dimensional numerical integration. However, in the
common case when a uniform prior is assigned to $\theta$, the marginal posterior
distribution of $\tau^{2}$ reduces to the prior, and only one numerical
integration is required.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{images/paper3/sup-example-applied-1}
\end{knitrout}
\caption{Probability of replication success as a function of relative sample
  size $c = n_{r}/n_{o}$ for experiment ``Labels'' with original effect estimate
  $\hat{\theta}_{o} = 0.205$ and standard error
  $\sigma_{o} = 0.051$ for uniform initial prior for effect size
  $\theta$ and either fixed $\tau = 0.05$ (as in main
  manuscript) or half normal prior with standard deviation
  $0.04$ assigned to $\tau$. Replication success is defined
  by the two-trials rule at level $\alpha = 0.025$, the replication
  Bayes factor at level $\gamma = 1/10$, fixed effects-meta
  analysis at level $\alpha = 0.025^{2}$, effect size
  equivalence based on $90\%$ confidence interval and with
  margin $\Delta = 0.2$, sceptical $p$-value at level
  $\alpha = 0.062$, and sceptical Bayes factor at level
  $\gamma = 1/10$.}
\label{fig:exampletaurandom}
\end{figure}
